No proof nets for MLL with units\\[5pt]\Large Proof equivalence in MLL is \textsc{pspace}-complete

### 2014-01-16 main/LICS.tex
hacks & fixes
rummaging around

\documentclass[conference]{IEEEtran}

@@

@@

@@

\noindent
The above proposition means that \MLL\ proof equivalence is the problem of deciding equivalence of proof nets.

@@

We will use a concise diagrammatic notation for sequents and proof nets.
%
The units $1$ and $\bot$ are represented by a circle $\circ$ and a disc $\bullet$ respectively.
%
A tensor is represented by a line connecting both subformulae, and a par by juxtaposition: if $A$ and $B$ are represented by \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-A.pdf}}
and \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-B.pdf}},
%
then $A\parr B$ is \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-AparB.pdf}}
and $A\tn B$ is \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-AtnB.pdf}}.
%
A tensor of multiple elements is denoted by stringing them together in a line, so $A\tn B\tn C$ is
\raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-AtnBtnC.pdf}}.
%
Boxes play the role of parentheses around par-formulae, so $(A\parr B)\tn C$ is drawn as \begin{center}{\includegraphics[scale=1]{hex-AparBtnC.pdf}}\end{center}

>>>>

\documentclass[conference,onecolumn]{IEEEtran}

@@

\let\alt=\underline

@@

%% STILL TO ADD:
%% - MLL proof equivalence is the word problem for *-autonomous categories
%% - IMLL proof equivalence is polynomial-time

@@

\noindent
The above proposition means that \MLL\ proof equivalence is the problem of deciding equivalence of proof nets.
%
% We will use proof net equivalence to encode constraint logic.

@@

We will use a concise diagrammatic notation for sequents and proof nets.
%
The units $1$ and $\bot$ are represented by a circle $\circ$ and a disc $\bullet$ respectively.
%
%
%% NEW
%
Formulae related by a tensor will be connected by edges, while formulae related by a par will be collected in a box, omitting an outer box for the complete sequent.
%
For example:
\[
	\bot\tn\bot,\bot\tn\bot,\1,(\1\parr\1\parr\1)\tn\bot
\]
\[
\begin{tikzpicture}[x=5mm,y=-5mm,octo]
	\draw (0,0) node[bullet] (a) {} -- (1,0) node[bullet] (b) {} (2,0) node[bullet] (c) {} -- (3,0) node[bullet] (d) {};
	\node[circ] (1) at (4,0) {};
	\node[circ] (2) at (5.5,0) {}; \node[circ] (3) at (6.5,0) {}; \node[circ] (4) at (7.5,0) {};
	\draw[rounded corners] (5,-1) rectangle (8,1);
	\draw (8,0) -- (9,0) node[bullet] (e) {};
\end{tikzpicture}
\]

\[
\begin{tikzpicture}[x=5mm,y=-5mm,octo]
	\node[circ] (1) at (6,0) {};
	\draw (0,0) node[bullet] (a) {} -- (1,0) node[bullet] (b) {} (3,0) node[bullet] (c) {} -- (4,0) node[bullet] (d) {};
	\node[circ] (2) at (1,3) {}; \node[circ] (3) at (2,3) {}; \node[circ] (4) at (3,3) {};
	\draw[rounded corners] (0,2) rectangle (4,4);
	\draw (4,3) -- (5,3) node[bullet] (e) {};
	\begin{scope}[thepink,->]
			\draw[bend right=10] (a) to (2);
			\draw[bend right=10] (b) to (3);
			\draw[bend left=10] (c) to (3);
			\draw[bend left=10] (d) to (4);
			\draw[bend right=10] (e) to (1);
	\end{scope}
\end{tikzpicture}
\]

%% OLD

%
A tensor is represented by a line connecting both subformulae, and a par by juxtaposition: if $A$ and $B$ are represented by \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-A.pdf}}
and \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-B.pdf}},
%
then $A\parr B$ is \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-AparB.pdf}}
and $A\tn B$ is \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-AtnB.pdf}}.
%
A tensor of multiple elements is denoted by stringing them together in a line, so $A\tn B\tn C$ is
\raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-AtnBtnC.pdf}}.
%
Boxes play the role of parentheses around par-formulae, so $(A\parr B)\tn C$ is drawn as \begin{center}{\includegraphics[scale=1]{hex-AparBtnC.pdf}}\end{center}
